---
title: "Simple Linear Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simple Linear Regression}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Package Objective
The goal of this package is to implement simple linear regression in C++ and integrate it into R. 

Simple linear regression solves the following least squares optimization problem:
\[
\hat{\beta}_0, \hat{\beta}_1 = \argmin_{\beta_0, \beta_1} ||\mathbf{y} - (\beta_0 + \beta_1 \cdot \mathbf{x})||_2.
\]

# Using the package
Suppose we have a vector of covariate observations $x$ and a vector of response observations $y$:
```{r}
x <- rnorm(100, 0, 1)
y <- 0.5 + 1.5 * x + rnorm(100, 0, 0.2)
```

We invoke the fitting C++ code via
```{r}
fit <- simplin::simp_lin_R(x, y)
```
which will return our estimates of $\hat{\beta}_0, \hat{\beta}_1$, standard errors and CIs for those parameters, and the fitted values and residuals.
These can be accessed by examining the returned list:
```{r}
str(fit)
```

It is of course necessary that the $x$ and $y$ vectors be numeric vectors of the same length, or else we'll get an error:
```{r}
x <- c(x, 1.1)
#NOT RUN:
#simplin::simp_lin_R(x, y) -- Error in simp_lin_R(x, y) : x and y must have the same length!
```